Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-18 paper/paper.tex
clarify ECDF

    \caption{Number of solved instances over CPU time for the eight algorithms we
        consider in this paper, and the virtual best solver (VBS) that shows the best
    solver on an instance by instance basis.\label{expTimeGraph}}
\end{figure}

@@

Figure~\ref{expTimeGraph} displays the evolution of the number of instances solved with respect to
CPU time. It shows us that the best solver depends on the time limit considered. \IncompleteLAD is
able to solve easy unsatisfiable instances very quickly, in a few milliseconds. Hence, for time
limits lower than \SI{5}{\ms}, the best solver is \IncompleteLAD. However, it is not able to solve harder
unsatisfiable instances, nor can it solve satisfiable instances.

@@

Figure~\ref{fig:portfolio-ecdf} shows the number of solved instances over time
for the individual solvers, the virtual best solver, and the \LLAMA algorithm
selection approach. The algorithm selection model does not perform well for
instances that can be solved quickly because of the overhead incurred through
feature computation.  As the instances become more difficult to solve, its
performance improves.

@@

\caption{Number of solved instances over time for the virtual best solver,
\LLAMA, and the single best solver \GlasgowTwo on the reduced set of 2336
instances. Other individual solvers are shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}. }
\label{fig:portfolio-ecdf}
\end{figure}

@@

Figure~\ref{fig:portfolio-ecdf-full} shows the number of solved instances over
time for the algorithm selection system including \IncompleteLAD and \VFtwo
presolving on the full set of instances. The performance on small instances is
much better than the \LLAMA selector alone (cf.\
Figure~\ref{fig:portfolio-ecdf}) and the region where \LLAMA performs worse than
the individual solvers is now limited to approximately $10^2$ to $10^5$
milliseconds.

@@

\begin{figure}[p]
    \input{graph-full}
\caption{Number of solved instances over time for the virtual best solver,
\LLAMA, and the single best solver \GlasgowTwo on the full set of 5725
instances. Other individual solvers are shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}. }
\label{fig:portfolio-ecdf-full}

>>>>

    \caption{Cumulative number of solved instances over CPU time for the eight algorithms we
        consider in this paper, and the virtual best solver (VBS) that shows the best
    solver on an instance by instance basis.\label{expTimeGraph}}
\end{figure}

@@

Figure~\ref{expTimeGraph} displays the evolution of the cumulative number of instances solved with respect to
CPU time. It shows us that the best solver depends on the time limit considered. \IncompleteLAD is
able to solve easy unsatisfiable instances very quickly, in a few milliseconds. Hence, for time
limits lower than \SI{5}{\ms}, the best solver is \IncompleteLAD. However, it is not able to solve harder
unsatisfiable instances, nor can it solve satisfiable instances.

@@

Figure~\ref{fig:portfolio-ecdf} shows the cumulative number of solved instances over time
for the individual solvers, the virtual best solver, and the \LLAMA algorithm
selection approach. The algorithm selection model does not perform well for
instances that can be solved quickly because of the overhead incurred through
feature computation.  As the instances become more difficult to solve, its
performance improves.

@@

\caption{Cumulative number of solved instances over time for the virtual best solver,
\LLAMA, and the single best solver \GlasgowTwo on the reduced set of 2336
instances. Other individual solvers are shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}. }
\label{fig:portfolio-ecdf}
\end{figure}

@@

Figure~\ref{fig:portfolio-ecdf-full} shows the cumulative number of solved instances over
time for the algorithm selection system including \IncompleteLAD and \VFtwo
presolving on the full set of instances. The performance on small instances is
much better than the \LLAMA selector alone (cf.\
Figure~\ref{fig:portfolio-ecdf}) and the region where \LLAMA performs worse than
the individual solvers is now limited to approximately $10^2$ to $10^5$
milliseconds.

@@

\begin{figure}[p]
    \input{graph-full}
\caption{Cumulative number of solved instances over time for the virtual best solver,
\LLAMA, and the single best solver \GlasgowTwo on the full set of 5725
instances. Other individual solvers are shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}. }
\label{fig:portfolio-ecdf-full}
